A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-07 manuscript.Rmd
added ref

```
---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
repro:
  scripts:
    - R/simulation.R
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
---
```

With the R version that you currently use, this specification is then translated into a `Dockerfile` that makes sure that the container image has all these packages installed.
The `Dockerfile` also contains the current date and fixes packages versions to the version of the package that were available on that day on the [Comprehensive R Archive Network (CRAN)](https://cran.r-project.org)[^cran] by relying on the [CRAN timemachine of Microsoft R Application Network (MRAN)](https://mran.microsoft.com/timemachine)[^mran].
<!-- Hands on: Introduce Docker -->

@@

Docker can be a bit unfriendly, because it requires a complicated mental model and some knowledge about how to install software on Linux.
An R-focused alternative is the R package [`renv`](https://rstudio.github.io/renv/articles/renv.html)[^renv][@R-renv].
`renv` isolates all R packages used in a project and records there version as well as the source from where they where installed.
This mechanism is faster and simpler to use than Docker, at the expense of only tracking R packages.
`renv` therefore is already of great use for reproducibility.
However, even when your project relies solely on R, external dependencies can still change the outcome of computations, like the operating system, the compilers used, the BLAS system in use and so forth.
Most importantly the R version itself has to match.

@@

To verify the data integrity, you can include a line of code after reading the data that looks like this:
<!-- AP: shouldn't this be wrapped into a repro function and also stored in the YAML header??? -->

```{r}
# create a dummy data.frame with two columns
x <- data.frame(VAR1 = c(1, 2, 3, 4), VAR2 = c(0, 4, 6, 9))
# compute hash using md5
hash <- digest::digest(x, "md5")
if(hash != "5ba412f5a26f43842971dd74954fcdeb"){
  warning("Mismatch between original and current data!\nHash now is:\n    '", hash, "'")
}
```

>>>>

```
---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
repro:
  scripts:
    - R/simulation.R
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
---
```
<!--AP emphasize more how cool it is that this stuff is automatically generated by repro!-->
With the R version that you currently use, this specification is then translated into a `Dockerfile` that makes sure that the container image has all these packages installed.
The `Dockerfile` also contains the current date and fixes packages versions to the version of the package that were available on that day on the [Comprehensive R Archive Network (CRAN)](https://cran.r-project.org)[^cran] by relying on the [CRAN timemachine of Microsoft R Application Network (MRAN)](https://mran.microsoft.com/timemachine)[^mran].
<!-- Hands on: Introduce Docker -->

@@

Docker can be a bit unfriendly, because it requires a complicated mental model and some knowledge about how to install software on Linux.
An R-focused alternative is the R package [`renv`](https://rstudio.github.io/renv/articles/renv.html)[^renv][@R-renv].
`renv` isolates all R packages used in a project and records there version as well as the source from where they where installed.
This mechanism is faster and simpler to use than Docker, at the expense of only tracking R packages.
`renv` therefore is already of great use for reproducibility [@vanlissa2020worcs].
However, even when your project relies solely on R, external dependencies can still change the outcome of computations, like the operating system, the compilers used, the BLAS system <!--AP reference, also explain what this is... most people will not know--> in use and so forth.
Most importantly the R version itself has to match. 
For example, @Peikert2019 illustrate how the generation of random numbers across different R versions is a threat to reproducibility.

@@

To verify the data integrity, you can include a line of code after reading the data that looks like this:
<!-- AP: shouldn't this be wrapped into a repro function and also stored in the YAML header??? -->
<!-- AP: can you demonstrate this with the actual openpsychometric data instead?-->
```{r}
# create a dummy data.frame with two columns
x <- data.frame(VAR1 = c(1, 2, 3, 4), VAR2 = c(0, 4, 6, 9))
# compute hash using md5
hash <- digest::digest(x, "md5")
if(hash != "5ba412f5a26f43842971dd74954fcdeb"){
  warning("Mismatch between original and current data!\nHash now is:\n    '", hash, "'")
}
```
